The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.

### 2022-09-02 src/tex/ms.tex
minor tex changes

% Title
% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation history  }
% \title{ A flexible expression for the metallicity-dependent cosmic star formation history: }
\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.}

@@

%%%%%%%%%%%%%%%
\author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
60 Garden St., Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{L. Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0003-3308-2420]{R. Pakmor}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract with filler text
\begin{abstract}
New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts. To interpret these observations we need to compare them to predictions from stellar population models. Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input. Large uncertainties remain in the shape and evolution of this function, and understanding its behaviour is essential to explain simulation results. 
% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
% Understanding the behaviour of the adopted metallicity distribution with which stars form is essential to explain simulation results. 
% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
In this work, we propose a simple analytical function for \SFRDzZ. 
% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
%
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are: I) the location of features is remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations. This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
% We further find that: III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution. 
% IV) the shape of the overall star-formation rate density has a small impact on the local mass distribution.
\end{abstract}

@@

\paragraph{The model allows for a controlled experiment on the effect of \SFRDzZ on the local distribution of merging BBH}
As an example, we apply our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}.
We systematically vary all five parameters that shape the cosmic metallicity density distribution, and explore two additional variations of the overall star-formation rate density \SFRDz.
Our main findings are as follows:
\begin{itemize}

    \item The location of features in the distribution of primary BH masses are robust against variations in \SFRDzZ. The location of features in the mass distribution of BHs could thus be used as sign posts of their formation channel.

    \item For all variations, the low mass end of the mass distribution is least influenced by changes in the \SFRDzZ.
    This is because the lowest mass BHs can be formed from all metallicities above $Z~\gtrsim~10^{-3}$, for which the star formation rate is relatively well constrained in the recent Universe. 
    This suggests that lower end of the BH mass distribution (component masses of $\leq 15\Msun$) is potentially very powerful for constraining the physics of the formation channels, irrespective of the cosmic star formation rate uncertainties.

    \item The metallicity distribution of star formation at low redshift primarily impacts the normalisation of the BBH merger rate. Changing the overall star-formation rate density, \SFRDz also affects the rate, but to a lesser degree. This underlines how low-metallicity star formation at low redshifts dominates the overall normalisation of the BBH merger rate.

>>>>

% Title
% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation history  }
% \title{ A flexible expression for the metallicity-dependent cosmic star formation history: }
% \title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.}
\title{The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.}

@@

%%%%%%%%%%%%%%%
\author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0002-1590-8551]{C. Conroy}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0003-3308-2420]{R. Pakmor}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{L. Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract 
\begin{abstract}
New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts, while also revealing new features in source property distributions.
To interpret these observations, we need to compare them to predictions from stellar population models. Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input. Large uncertainties remain in the shape and evolution of this function.%and understanding its behaviour is essential to explain simulation results. 
In this work, we propose a simple analytical function for \SFRDzZ. 
Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. 
%Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are: I) the locations of features are remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations. This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
% We further find that: III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution. 
% IV) the shape of the overall star-formation rate density has a small impact on the local mass distribution.
\end{abstract}

@@

\paragraph{The model allows for a controlled experiment on the effect of \SFRDzZ on the local distribution of merging BBH}
As an example, we use our model to calculate the local rate and mass distribution of the more massive components from merging BBHs (\Mbheen) in Figures \ref{fig: stable mass dists} and \ref{fig: CE mass dists}.
We systematically vary all five parameters that shape the cosmic metallicity density distribution, and explore two additional variations of the overall star-formation rate density \SFRDz.
Our main findings are as follows:
\begin{itemize}

    \item The locations of features in the distribution of primary BH masses are robust against variations in \SFRDzZ. The location of features in the mass distribution of BHs could thus be used as sign posts of their formation channel.

    \item For all variations, the low mass end of the mass distribution is least influenced by changes in the \SFRDzZ.
    This is because the lowest mass BHs can be formed from all metallicities above $Z~\gtrsim~10^{-3}$, for which the star formation rate is relatively well constrained in the recent Universe. 
    This suggests that the lower end of the BH mass distribution (component masses of $\leq 15\Msun$) is potentially very powerful for constraining the physics of the formation channels, irrespective of the cosmic star formation rate uncertainties.

    \item The metallicity distribution of star formation at low redshift primarily impacts the normalisation of the BBH merger rate. Changing the overall star-formation rate density, \SFRDz also affects the rate, but to a lesser degree. This shows that low-metallicity star formation at low redshifts dominates the overall normalisation of the BBH merger rate.
